Simulated Observations of Young Protoplanetary Discs

### 2013-02-07 paper.tex
minor tweaks

To simulate observations, the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and the disc is inclined at 30$^\circ$ to edge on. From these simulated observations, integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
The simulations were focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
(Note the integrated intensity and intensity weighted velocity maps (figures \ref{sim_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams  (figure \ref{pvs}) as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions})\newline

@@

\begin{figure*}
 \includegraphics[width=150mm]{Figures/sim/imageALL_30deg_all.eps}
 \caption{{\bf Left:}Continuum subtracted integrated intensity maps, {\bf Right:} Intensity weighted velocity maps. The spiral structure in different regions of the disc is highlighted by looking at different molecular lines. From top to bottom the lines displayed are: OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2. All maps are integrated over -12.5 to -0.5 and 0.5 to 12.5 in order to avoid the envelope contribution.}
 \label{sim_all}
\end{figure*}

>>>>

To simulate observations, the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and the disc is inclined at 30$^\circ$ to edge on. From these simulated observations, integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
We focus on the frequency range available with ALMA, with particular attention to band 7, which offers the best trade off between resolution and sensitivity.
(Note the integrated intensity and intensity weighted velocity maps (figures \ref{sim_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams  (figure \ref{pvs}) as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions})\newline

@@

\begin{figure*}
 \includegraphics[width=150mm]{Figures/sim/imageALL_30deg_all.eps}
 \caption{{\bf Left:}Continuum subtracted integrated intensity maps, {\bf Right:} Intensity weighted velocity maps. The spiral structure in different regions of the disc is highlighted by looking at different molecular lines. From top to bottom the lines displayed are: OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2. All maps are integrated over -12.5 to -0.5 and 0.5 to 12.5 km$\,$s$^{-1}$ in order to avoid the envelope contribution.}
 \label{sim_all}
\end{figure*}
